Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-02 manuscripts/paper-1/main.tex
Again grammer check, and mapping added

    Digital twins are highly intricate and adaptable systems that possess the capability to not only respond to environmental 
    changes but also modify their internal structure \cite{ZHANGUPDATEMETHOD,MobusSystemTheory}. Therefore, ascertaining a 
    requisite level of quality for the construction of a digital twin is an arduous undertaking.

@@

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features. 
    These updates and new features will result in definite changes to the structure of the system. 
    On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout 
    depending on the user's hardware. As we have seen in \cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems, 
    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis,
    reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
    \section{Artifacts and Methods}
    The used methodology consists of manual artifact reviews and evaluation of the results according to the digital twin quality attributes.    
    \subsection{Artifacts}
    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \subsection{Manual Artifact Reviews and Evoluation}
    During the initial stages of the project, when the target system was not yet available, there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
    The manual review included, audits, inspections, reviews, structural analysis 
    and walkthroughs with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}. Lastly, identified issues after the reviews were mapped to the quality attributes.

    \section{Results}
    During the initial stages of the project, when the target system was not yet available, there was a 
    lack of observable data about system behavior that could be utilized for validation. Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
    Therefore, manual reviews for each artifact were conducted and twenty-one issues were identified and mapped to the specific digital twin quality attributes. 
    The analysis revealed that a total of thirty-eight digital twin quality attributes were lacking in these artifacts. \ref{fig:QualityInspectonResultsWithArtifacts}

@@

F3-  Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
Also, standard categories were considered as a cause of requirements instead of a category of requirements. Furthermore, 
the constraint category was considered a non-functional requirement which results in a significant misunderstanding between non-functional 
requirements and constraints. Finally, some requirements were described as non-functional requirements instead of functional requirements.

@@

F13:The input controls in the Discrete  Event Simulation module were not complete or aligned with the actual inputs that will be provided by another system.

F14, F15:The ranges defined for some events were not validated.

F16:Database structures were not updated automatically, instead done manually.

F17:The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.

F18:Discerete Event Simulation module does not support parallel execution of micro-operations.

F19:Interruption mechanism of the assembly line was not considered within the DES module.

F20:Number of micro-operations were hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.

F21:Edge-cases were not considered in the DES module.

>>>>

    Digital twins are highly intricate and adaptable systems that possess the capability to not only respond to environmental 
    changes but also modify their internal structure \cite{ZHANGUPDATEMETHOD, MobusSystemTheory}. Therefore, ascertaining a 
    requisite level of quality for the construction of a digital twin is an arduous undertaking.

@@

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features. 
    These updates and new features will result in definite changes to the structure of the system. 
    On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout 
    depending on the user's hardware. As we have seen in \cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems, 
    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis,
    reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%METHODS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Artifacts and Methods}
    The used methodology consists of manual artifact reviews and evaluation of the results according to the digital twin quality attributes.    
    \subsection{Artifacts}
    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \subsection{Manual Artifact Reviews and Evoluation}
    During the initial stages of the project, when the target system was not yet available, there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
    The manual review included, audits, inspections, reviews, structural analysis 
    and walkthroughs with the project partners which was inspired by Balci's manual review works \cite{balcitechniques}. Lastly, identified issues after the reviews were mapped to the quality attributes. 
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Results}
    During the initial stages of the project, when the target system was not yet available, there was a 
    lack of observable data about system behavior that could be utilized for validation. Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
    Therefore, manual reviews for each artifact were conducted and twenty-one issues were identified and mapped to the specific digital twin quality attributes. 
    The analysis revealed that a total of thirty-eight digital twin quality attributes were lacking in these artifacts. \ref{fig:QualityInspectonResultsWithArtifacts}

@@

    F3 - Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
    Also, standard categories were considered as a cause of requirements instead of a category of requirements. Furthermore, 
    the constraint category was considered a non-functional requirement which results in a significant misunderstanding between non-functional 
    requirements and constraints. Finally, some requirements were described as non-functional requirements instead of functional requirements.

@@

    F13 - The input controls in the discrete event simulation module was not complete or aligned with the actual inputs that will be provided by another system.

    F14, F15 - The ranges defined for some events were not validated.

    F16 - Database structures were not updated automatically, instead done manually.

    F17 - The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.

    F18 - Discrete event Simulation module does not support parallel execution of micro-operations.

    F19 - The interruption mechanism of the assembly line was not considered within the DES module.

    F20 - The number of micro-operations was hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.

    F21 - Edge cases were not considered in the DES module.

    \subsection{Mapping Issues to Quality Attributes}

    \begin{table}[h!]
        \begin{center}
          \caption{Mapping Findings to Quality Attributes}
          \label{tab:Mapping}
          \begin{tabular}{l@{\hspace{1cm}}l} 
            \textbf{Findings} & \textbf{Quality Issues}\\
            \hline
            Finding 1 &     Completeness\\
            Finding 2 &     Completeness\\
            Finding 3 &     Correctness, Completeness\\
            Finding 4 &     Correctness\\
            Finding 5 &     Evolvability\\
            Finding 6 &     Completeness\\
            Finding 7 &     Correctness, Completeness, Fidelity, Efficiency, Evolvability\\
            Finding 8 &     Completeness, Fidelity, Evolvability\\
            Finding 9 &     Evolvability\\
            Finding 10 &    Correctness, Completeness, Fidelity, Evolvability\\
            Finding 11 &    Evolvability\\
            Finding 12 &    Correctness, Completeness\\
            Finding 13 &    Completeness, Evolvability\\
            Finding 14 &    Correctness, Completeness\\
            Finding 15 &    Correctness, Completeness\\
            Finding 16 &    Evolvability \\
      Finding 17&CorrectnessCompleteness \\
      Finding 18&CorrectnessEfficiency \\
      Finding 19&CompletenessEvolvability \\
      Finding 20&Evolvability \\
      Finding 21&Evolvability 
    \end{tabular}
    \end{center}
    \end{table}
